Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-04-17 manuscript/manuscript.qmd
Use {tinytable}!

```{r libraries-data}
library(tidyverse)
library(scales)
library(sf)
library(lubridate)
library(tidybayes)
library(marginaleffects)
library(patchwork)
library(colorspace)
library(kableExtra)
library(gt)
library(targets)

@@

```{r tbl-derogation-countries}
#| tbl-cap: Countries that derogated from the ICCPR in order to undertake pandemic-related emergency measures 
#| include: true
#| echo: false
bind_cols(dplyr::slice(map_data_nice, 1:12),
          add_row(dplyr::slice(map_data_nice, 13:n()))) %>% 
  kbl(booktabs = TRUE, linesep = "\\addlinespace[0.5em]",
      col.names = rep(c("Country", "Derogations"), 2)) %>% 
  kable_styling(font_size = ifelse(fmt_out == "latex", 8.5, NA))
```

>>>>

```{r libraries-data}
library(tidyverse)
library(scales)
library(sf)
library(lubridate)
library(tidybayes)
library(marginaleffects)
library(patchwork)
library(colorspace)
library(tinytable)
library(kableExtra)
library(targets)

@@

```{r tbl-derogation-countries}
#| tbl-cap: Countries that derogated from the ICCPR in order to undertake pandemic-related emergency measures 
#| include: true
#| echo: false
#| message: false

bind_cols(dplyr::slice(map_data_nice, 1:12),
          add_row(dplyr::slice(map_data_nice, 13:n()))) %>%
  set_names(c("Country", "Derogations", "Country", "Derogations")) %>% 
  tt(width = c(0.35, 0.15, 0.35, 0.15) * 0.9) %>% 
  format_tt() %>% 
  style_tt(j = 1:4, align = "lrlr") %>% 
  style_tt(
    bootstrap_class = "table table-sm table-striped",
    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}"
  )
```
